Modern Graph Generators: A Survey

### 2018-09-09 generators.tex
Refactored graph streaming and community detection into others section
Minor corrections

...

\input{data_sets}

@@

\input{generators_streaming}

>>>>

In this section we explore in more detail different graph data generators using the classification introduced before. For each category we briefly describe key features of each of the representatives. The aim is to provide the readers with a detailed look at each of the tools in the context of its competitors from the same domain.

@@

\input{generators_others}
